The SMT Competition 2015--2018

### 2019-08-31 2018/report/table-winners-main-families.tex
Remove 2015 column

\begin{table}
  \caption{Alternative best solvers in the \maintrack if the notion of families were implemented as stated in the rules, i.e., top most directory instead of bottom most.}
  \label{tab:results:total:top}
  \centering
  \scalebox{.755}{%
    \renewcommand{\arraystretch}{1.01}%

\begin{tabular}{r>{\columncolor{white}[.25em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l}
\toprule
Division & \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2015} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2016} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017} &                    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018} \\
\midrule
  AUFLIRA  &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\hspace*{5em}} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire [Z3]} \\
AUFNIRA  &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &              \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
BV       &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{q3b} Q3B} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
QF\_IDL   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} \\
QF\_LIA   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [MathSAT]} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [MathSAT]} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
QF\_NRA   &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
UFBV     &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &              \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
UFIDL    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
UFLIA    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
UFNIA    &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                 \hspace*{3em}        & \cc{vamp} Vampire [Z3] \\
\bottomrule
\end{tabular}
  }
\end{table}

>>>>

\begin{table}
  \caption{Alternative best solvers in the \maintrack if the notion of families had been implemented as stated in the rules, i.e., top most directory instead of bottom most}
  \label{tab:results:total:top}
  \centering
  \scalebox{.755}{%
    \renewcommand{\arraystretch}{1.01}%

\begin{tabular}{r>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l>{\columncolor{white}[.5em][.8em]}r@{\hskip .8em}|@{\hskip .5em}>{\columncolor{white}[.5em][.5em]}l}
\toprule
Division &                         \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2016} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2017} &                    \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{2018} \\
\midrule
AUFLIRA  &                             \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{vamp} Vampire [Z3]} \\
AUFNIRA  &               \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
BV       &                             \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{q3b} Q3B} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
QF\_IDL  &                             \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &       \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} &   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [Z3]} \\
QF\_LIA  &   \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [MathSAT]} &  \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{yices} Yices [MathSAT]} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
QF\_NRA  &                             \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
UFBV     &               \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
UFIDL    &          \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                        \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} \\
UFLIA    &                             \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &     \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{\cc{cvc4} CVC4 [Z3]} \\
UFNIA    &                             \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                            \multicolumn{2}{>{\columncolor{white}[.5em][.5em]}c}{} &                                 \hspace*{3em}        & \cc{vamp} Vampire [Z3] \\
\bottomrule
\end{tabular}
  }
\end{table}
